---
title: "Broockman and Kalla PAP"
output: html_document
---

```{r setup, include=FALSE}
# knitr setup options
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

# load packages
# step 1: run the next line in R to install the required packages
# install.packages(c("tidyverse", "DeclareDesign"))
library(tidyverse)
library(DeclareDesign)
```

URL for the paper: http://tinyurl.com/broockmankalla


# Overview


# Research question


# Hypotheses


# Research design


## Model

1. Declare the study *population*. We'll treat Broockman and Kalla's baseline survey as our study population. If you are missing key characteristics of your study population, you can add them here, below data.

Description in text

```{r, cache = TRUE}
# load the Broockman-Kalla baseline data
bk_baseline <- read_rds(url("https://www.dropbox.com/s/8hx0fvk8ocym7te/broockman-kalla.RDS?dl=1"))
```

```{r}
my_population <- declare_population(
  data = bk_baseline
  # you can add variables here like:
  # young_indicator = if_else(vf_age < 21)
)
```

2. Declare the *potential outcomes*. What are your outcomes? What are expected treatment effect sizes? Are there heterogeneous effects? Define a set of potential outcomes for each key outcome you plan to measure.

Description in text

```{r}
my_potential_outcomes <- declare_potential_outcomes(

)
```

## Inquiry

Declare the estimand(s) -- what are the causal questions the study is trying to assess

Description in text

```{r}
my_estimand_1 <- declare_estimand(
  
)
```

## Data strategy

### Sampling and case selection

Description in text

```{r}
# If your sample is the same as the population, you can delete the code below
my_sampling <- declare_sampling(
  
)
```

### Treatment assignment

Description in text

For some random assignment function options, head to https://declaredesign.org/r/randomizr/articles/randomizr_vignette.html

```{r}
my_assignment_1 <- declare_assignment(
  
)
```


### Outcomes

Description in text 

```{r}
outcomes <- declare_reveal(outcome_variables = c(), 
                           assignment_variables = Z)
```

## Answer strategy

Description in text 

```{r}
estimator1 <- declare_estimator(
  
)
```

## Design declaration

```{r, eval = FALSE}
study_design <- 
  population + 
  # add more steps here
  # then switch eval to TRUE
```

# Diagnosis

```{r, eval = FALSE}
# when your design is ready, set eval to TRUE
diagnosis <- diagnose_design(study_design, sims = 1000)
```

```{r, eval = FALSE}
# when your design is ready, set eval to TRUE
# this will print out a simple table of your diagnosands
kable(get_diagnosands(diagnosis))
```

# Ethics



# Mock results

```{r, eval = FALSE}
# when your design is ready, set eval to TRUE
# these two lines create a simulated data frame and a simulated data frame of *estimates*
# use them to code up the tables and figures you want to include in the PAP
mock_data <- draw_data(study_design)
mock_estimates <- draw_estimates(study_design)
```

